---
title: "MATH 216 Homework 2 Shiny App"
author: "Yuchen Zhu"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(babynames)
library(ggplot2movies)
```


## Question 2:

In the file `HW-2_Shiny_App.Rmd`, build the Shiny App discussed in Lec09 on
Monday 10/3: Using the `movies` data set in the `ggplot2movies` data set, make a Shiny app that

* Plots budget on the x-axis and rating on the y-axis
* Instead of having a radio button to select the genre of movie (`Action`,  `Animation`, `Comedy`, etc), have a radio button that allows you to toggle
between comedies and non-comedies. This app should be simpler.

```{r eruptions, echo=FALSE}
inputPanel(
  radioButtons("genre", label = "Genre:",
               choices = c("Comedy", "Non_Comedy"), selected = "Comedy")
)

renderPlot({
  
  movies <- ggplot2movies::movies %>% 
    mutate(Non_Comedy = ifelse(Comedy != 1, 1, 0))
  
  movies_genre <- movies %>%
    select_("budget", "rating", input$genre) %>% 
    filter(!is.na(budget)) %>% 
    rename_("type"=input$genre) %>% 
    filter(type == 1)
  
  ggplot(movies_genre, aes(x = budget, y = rating)) +
    geom_point() +
    scale_x_log10()
})
```